### 2011-07-12 doc/theses/svirec/kap3.tex
another part of the proposed algorithm

\begin{define}[Weak satisfiability]
Let $RXT = \langle T, \delta, \varrho \rangle$ be an R-XML tree conforming a DTD $D$, and $f: S \rightarrow p$ be a functional dependency. We say that $RXT$ weakly satisfies $f$ ($RXT \models_w f$) if one of the following conditions holds:
\begin{enumerate}
	\item $\langle T, \delta \rangle \models f$;
    \item for each pair of tuples $t_1$, $t_2$ of $RXT$ one of the following holds:
    \begin{enumerate}
    	\item there exists a path $p_i \in S$ such that: \\
$(\varrho(p_i(t_1)) = false) \lor (\varrho(p_i(t_2)) = false)$;
        \item $(\varrho(p(t_1)) = false) \lor (\varrho(p(t_2)) = false)$.\qed
    \end{enumerate}
\end{enumerate}
\end{define}

>>>>

\begin{define}[Weak satisfiability]\label{weakSatisf}
Let $RXT = \langle T, \delta, \varrho \rangle$ be an R-XML tree conforming a DTD $D$, and $f: S \rightarrow p$ be a functional dependency. We say that $RXT$ weakly satisfies $f$ ($RXT \models_w f$) if one of the following conditions holds:
\begin{enumerate}
	\item $\langle T, \delta \rangle \models f$;
    \item for each pair of tuples $t_1$, $t_2$ of $RXT$ one of the following holds:
    \begin{enumerate}
    	\item there exists a path $p_i \in S$ such that: \\
$(\varrho(p_i(t_1)) = false) \lor (\varrho(p_i(t_2)) = false)$;
        \item $(\varrho(p(t_1)) = false) \lor (\varrho(p(t_2)) = false)$.\qed
    \end{enumerate}
\end{enumerate}
\end{define}
